First round comments from the Ad-hoc rewiew committee \\ (Maurik Holtrop, Kevin Giovankl, Zein-Eddine Meziani)

### 2018-08-10 eg6-letters/incoherent/adhocreview/1st_adhoc_comments.tex
first response to the adhon comments

\item    For figure 6, you state that "our experiment shows a sharp drop" (line 
   250), in the incoherent $A_{LU}$/proton $A_{LU}$. You do indeed have a 
      single point, at the lowest $x_B$, that is lower than the other three, 
      but it seems that I can draw a straight horizontal line through all 4 
      error bars. It seems too strong a statement to speak of a sharp drop 
      here, and subsequently conclude that there is "strong quenching of the 
      BSA" (line 253). If I contrast this graph with figure 5, where you state 
      that "$A_{LU}$ does not indicate a strong dependence on $Q^2$", I agree 
      with you. The variation between the point in figure 5 is however similar 
      to that in figure 6, except the order of the variation is different.\\ 
      \textcolor{blue}{ }

\item    To further consider this statement, I looked up ref. 21, which 
   contains the proton data that you divide by. This data is not, however, 
      shown as a function of $x_B$, but in a set of tiles, with variation in -t 
      shown for different $x_B$ and $Q^2$ average values. It is then not quite 
      clear how you used this data to get the data points to divide out the 
      proton $A_{LU}$. How closely do the kinematics agree? How does this 
      procedure affect the systematic uncertainties? This is important 
      information to make a judgement on the validity of your figure6.\\
   \textcolor{blue}{ }

\item  The paper makes no mention of the initial momentum of the struck 
   nucleon, which I would expect to smear out the kinematics. It would be 
      useful for the reader to get an impression on how large this effect would 
      be. Does this explain the widths of the distributions in figure 2, or are 
      these widths dominated by detector resolution?\\
   \textcolor{blue}{ }

\item    There is also no mention of final state interactions in the paper. It 
   is not obvious to me that the FSA should be zero for a beam spin asymmetry 
      on 4He. If you have a calculation that shows this is the case, it would 
      be good to mention it.\\
   \textcolor{blue}{ }

@@

>>>>

\item    For figure 6, you state that "our experiment shows a sharp drop" (line 
   250), in the incoherent $A_{LU}$/proton $A_{LU}$. You do indeed have a 
      single point, at the lowest $x_B$, that is lower than the other three, 
      but it seems that I can draw a straight horizontal line through all 4 
      error bars. It seems too strong a statement to speak of a sharp drop 
      here, and subsequently conclude that there is "strong quenching of the 
      BSA" (line 253). If I contrast this graph with figure 5, where you state 
      that "$A_{LU}$ does not indicate a strong dependence on $Q^2$", I agree 
      with you. The variation between the point in figure 5 is however similar 
      to that in figure 6, except the order of the variation is different.\\ 
      \textcolor{red}{Should we keep it then? }

\item    To further consider this statement, I looked up ref. 21, which 
   contains the proton data that you divide by. This data is not, however, 
      shown as a function of $x_B$, but in a set of tiles, with variation in -t 
      shown for different $x_B$ and $Q^2$ average values. It is then not quite 
      clear how you used this data to get the data points to divide out the 
      proton $A_{LU}$. How closely do the kinematics agree? How does this 
      procedure affect the systematic uncertainties? This is important 
      information to make a judgement on the validity of your figure6.\\
   \textcolor{blue}{For this specific purpose, we applied four dimensional 
      binning to our incoherent DVCS data to get kinematical mean values close 
      to the published free proton results. The review committee members are 
      invited to check our kinematical distributions in 
      fig.~\ref{fig:incoh-kin} for the shown bins in FIG.~6 in the PRL and the 
      free proton data highlighted in figure \ref{fig:free-p}. }

\begin{figure}[h!]
   \includegraphics[width=14.9cm]{t_InCoh_bins.pdf}
   \caption{The t, $Q^2$ and $x_{B}$ distributions for the incoherent DVCS bins 
   shown in figure 6 in the prl.}
\label{fig:incoh-kin}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=14.9cm]{e1dvcs1_free_proton_alu.pdf}
   \caption{The free proton published beam-spin asymmetries. The highlighted 
   data points are the ones used to construct the beam-spin asymmetry rations 
   in FIG.~6 in the PRL.}
\label{fig:free-p}
\end{figure}

\item  The paper makes no mention of the initial momentum of the struck 
   nucleon, which I would expect to smear out the kinematics. It would be 
      useful for the reader to get an impression on how large this effect would 
      be. Does this explain the widths of the distributions in figure 2, or are 
      these widths dominated by detector resolution?\\
   \textcolor{blue}{We have studied this effect in details. The review 
      committee members are invited to check appendix H in the analysis note 
      \url{ 
      https://www.jlab.org/Hall-B/shifts/index.php?display=admin&task=paper_review&rid=7619165&operation=view}.}

\item  There is also no mention of final state interactions in the paper. It is 
   not obvious to me that the FSA should be zero for a beam spin asymmetry on 
      4He. If you have a calculation that shows this is the case, it would be 
      good to mention it.\\
   \textcolor{blue}{There are no such theoretical calculations of the FSI on 
      the incoherent DVCS asymmetries on the $^4$He. }

@@

\newpage
\newpage
\newpage
\newpage
